Governing through patronage: the bargain for education in decentralized Brazil

### 2020-09-30 paper/paper.tex
create outline for intro

Across the world, vulnerable populations rely on governments for access to basic public services such as education. In the developing world, the quality of public education remains woefully low: functional illiteracy remains widespread, basic mathematical operations.\footnote{The World Bank calls this ``learning poverty". See \url{https://www.worldbank.org/en/topic/education/brief/learning-poverty}}. Clearly, politicians play an important role in delivering these services \citep{gulzar_politicians_2017,besley_political_2003}, but what are the incentives they face and what are their implications for bureaucratic institutions responsible for delivering them. \citep{cochrane_policies_1983, falleti_decentralization_2010}. How can local governments improve the quality the of public services they deliver? In particular, how do political actors reshape bureaucratic institutions, and what are their downstream consequences for student learning?

The quality of public education in the across the world, and particularly in the developing world, remains low: functional illiteracy is widespread, children cannot perform arithmetic operations. How can public education be improved?

Previous studies have found that certain incentives, whether these be electoral or performance-related, can help raise the quality of public services \citep{gulzar_politicians_2017,duflo_incentives_2012}. Often relying on individualized interventions, these studies provide compelling evidence that political and bureaucratic actors respond to policy changes.\citep{finan_personnel_2015} But how do these actors relate to one another in local institutions? Who holds power over public education, and whose interests is it meant to serve?

>>>>

Across the world, vulnerable populations rely on governments for access to basic public services such as education. In the developing world, the quality of public education remains low: functional illiteracy is widespread, basic mathematical operations beyond the reach of most. This ``learning poverty'' is in  How can local governments improve the quality the of public services they deliver? In particular, how do political actors reshape bureaucratic institutions, and what are their downstream consequences for student learning.
